child expenditure

### 2024-02-14 child_expendure_graphs.qmd
fixed medicaid graph y axisy

# medicaid benefits
ggplot(child_enforce_data, aes(x = year, y = aca_mcaid_exp)) +
  geom_col(fill = "#1f77b4" ) + labs(x = "Year", y = "Number of people who have ACA Medicaid Expenditure", title = "People who have ACA Medicaid Expenditure Over Time (Years)") + theme_minimal() +  theme(plot.title = element_text(hjust = 0.5))  
```

>>>>

# medicaid benefits
ggplot(child_enforce_data, aes(x = year, y = aca_mcaid_exp)) +
  geom_col(fill = "#1f77b4" ) + labs(x = "Year", y = "Number of people with ACA Medicaid Expenditure", title = "People who have ACA Medicaid Expenditure Over Time (Years)") + theme_minimal() +  theme(plot.title = element_text(hjust = 0.5))  
```
